Imputation of Incomplete Multilevel Data with \pkg{mice}

### 2022-04-11 Manuscript/Imputation_of_Incomplete_Multilevel_Data.Rmd
Feedback on cleaned up manuscript (add popularity case study back in!)

\begin{table}[tb]
\caption{Concepts in multilevel methods}
\label{tab:clus}
\centering
\begin{tabular}{ll}
\hline
\textbf{Concept} & \textbf{Details}   \\
\hline
ICC                 & The variability due to clustering is often measured by means of the \\
                    & intraclass coefficient (ICC). The ICC can be seen as the percentage \\
                    & of variance that can be attributed to the cluster-level, where a high \\
                    & ICC would indicate that a lot of variability is due to the cluster \\
                    & structure. \\
Random intercept    & Multilevel models typically accommodate for variability by including \\
                    & a separate group mean for each cluster. In addition to random \\
                    & intercepts, multilevel models can also include random effects and \\
                    & heterogeneous residual error variances across clusters [see e.g. \\
                    & @gelm06, @hox17 and @jong21]. \\
\hline
\end{tabular}
\end{table}

@@

\begin{table}[tb]
\caption{Concepts in missing data methods}
\label{tab:miss}
\centering
\begin{tabular}{ll}
\hline
\textbf{Concept} & \textbf{Details}   \\
\hline
MCAR    & Missing Completely At Random, where the probability to be missing is equal \\
& across all data entries \\
MAR     & Missing At Random, where the probability to be missing depends on observed \\
& information \\
MNAR    & Missing Not At Random (MNAR), where the probability to be missing \\
& depends on unrecorded information, making the missingness non-ignorable \\
& [@rubi76; @meng94]. \\
& [TODO: add congeniality.] \\
\hline
\end{tabular}
\end{table}

@@

\begin{table}[tb]
\caption{Concepts in missing data methods}
\label{tab:mod}
\centering
\begin{tabular}{ll}
\hline
\textbf{Concept} & \textbf{Details}   \\
\hline
& [TODO: explain \pkg{lme4} notation here] \\
\hline
\end{tabular}
\end{table}

@@

The `impact` data included in the \pkg{metamisc} package is a complete data set. The original data has already been imputed once (Steyerberg et al, 2008). For the purpose of this tutorial we have induced missingness (mimicking the missing data in the original data set before imputation). The resulting incomplete data can be accessed from [zenodo link to be created](https://zenodo.com).

@@

```{r forest, echo=FALSE}
fits <-
  purrr::map_dfr(
    unique(impact$name),
    ~ {
      glm(
        mort ~ 1 + age + motor_score + pupil + ct,
        family = "binomial",
        data = filter(impact, name == .x)
      )
    } %>%
      broom::tidy(conf.int = TRUE, exponentiate = TRUE) %>%
      .[, c("term", "estimate", "conf.low", "conf.high")] %>%
      cbind(name = as.character(.x), .)
  )
filter(fits, term %in% c("ctIII")) %>% #, "ctIV/V"
  ggplot(aes(y = name, x = estimate)) +
  geom_vline(xintercept = 1, size = 1.5, color = "grey95") +
  geom_point() +
  geom_linerange(aes(y = name, xmin = conf.low, xmax = conf.high)) +
  labs(y = "Study", x = "Odds ratio", color = NULL) +
  theme_classic()
```

@@

This shows... [TODO: fill in that we need to impute `ct` and `pupil`.]

>>>>

\begin{table}[tb]
\caption{Concepts in multilevel methods}
\label{tab:clus}
\centering
\begin{tabular}{ll}
\hline
\textbf{Concept} & \textbf{Details}   \\
\hline
ICC                 & The variability due to clustering is often measured by means of the \\
                    & intraclass coefficient (ICC). The ICC can be seen as the percentage \\
                    & of variance that can be attributed to the cluster-level, where a high \\
                    & ICC would indicate that a lot of variability is due to the cluster \\
                    & structure. \\
Random effect       & Multilevel models typically accommodate for variability by including \\
                    & a separate group mean for each cluster. In addition to random \\
                    & intercepts, multilevel models can also include random effects and \\
                    & heterogeneous residual error variances across clusters [see e.g. \\
                    & @gelm06, @hox17 and @jong21]. TODO: add stratification. \\
\hline
\end{tabular}
\end{table}

@@

\begin{table}[tb]
\caption{Concepts in missing data methods}
\label{tab:miss}
\centering
\begin{tabular}{ll}
\hline
\textbf{Concept} & \textbf{Details}   \\
\hline
MCAR    & Missing Completely At Random, where the probability to be missing is equal \\
& across all data entries \\
MAR     & Missing At Random, where the probability to be missing depends on observed \\
& information \\
MNAR    & Missing Not At Random (MNAR), where the probability to be missing \\
& depends on unrecorded information, making the missingness non-ignorable \\
& [@rubi76; @meng94]. \\
& [TODO: add congeniality, but maybe in-text?] \\
\hline
\end{tabular}
\end{table}

@@

\begin{table}[tb]
\caption{Notation}
\label{tab:mod}
\centering
\begin{tabular}{ll}
\hline
\textbf{Concept} & \textbf{Details}   \\
\hline
& [TODO: explain \pkg{lme4} notation here] \\
\hline
\end{tabular}
\end{table}

TODO: add paragraph about novice and more experienced readers.

@@

The `impact` data included in the \pkg{metamisc} package is a complete data set. The original data has already been imputed once (Steyerberg et al, 2008). For the purpose of this tutorial we have induced missingness (mimicking the missing data in the original data set before imputation). The resulting incomplete data can be accessed from [zenodo link to be created](https://zenodo.com). TODO: email script to thomas.

@@

```{r forest, echo=FALSE}
fits <-
  purrr::map_dfr(
    unique(impact$name),
    ~ {
      glm(
        mort ~ 1 + age + motor_score + pupil + ct,
        family = "binomial",
        data = filter(impact, name == .x)
      )
    } %>%
      broom::tidy(conf.int = TRUE, exponentiate = TRUE) %>%
      .[, c("term", "estimate", "conf.low", "conf.high")] %>%
      cbind(name = as.character(.x), .)
  )
filter(fits, term %in% c("ctIII")) %>% #, "ctIV/V"
  ggplot(aes(y = name, x = estimate)) +
  geom_vline(xintercept = 1, size = 1.5, color = "grey95") +
  geom_point() +
  geom_linerange(aes(y = name, xmin = conf.low, xmax = conf.high)) +
  labs(y = "Study", x = "Adjusted odds ratio for ct", color = NULL) +
  theme_classic()
# TODO: add heterogeneity in distribution of ct -> prevalence in ct across clusters with CI
# TODO: missingness prop inside clusters
# TODO: make row height proportional to pattern frequency
```

@@

This shows... [TODO: fill in that we need to impute `ct` and `pupil`.] TODO: remove axis labels

### 2022-04-11 Manuscript/Imputation_of_Incomplete_Multilevel_Data.tex
Feedback on cleaned up manuscript (add popularity case study back in!)

\begin{CodeChunk}
\begin{CodeInput}
R> mod <- mort ~ 1 + type + age + motor_score + pupil + ct + (1 | name)
\end{CodeInput}
\end{CodeChunk}

@@

The \texttt{impact} data included in the \pkg{metamisc} package is a
complete data set. The original data has already been imputed once
(Steyerberg et al, 2008). For the purpose of this tutorial we have
induced missingness (mimicking the missing data in the original data set
before imputation). The resulting incomplete data can be accessed from
\href{https://zenodo.com}{zenodo link to be created}.

@@

This shows\ldots{} {[}TODO: fill in that we need to impute \texttt{ct}
and \texttt{pupil}.{]}

>>>>

\begin{CodeChunk}
\begin{CodeInput}
R> mod <- mort ~ 1 + type + age + motor_score + pupil + ct + (1 | name) # TODO: add random effects ct?
\end{CodeInput}
\end{CodeChunk}

@@

The \texttt{impact} data included in the \pkg{metamisc} package is a
complete data set. The original data has already been imputed once
(Steyerberg et al, 2008). For the purpose of this tutorial we have
induced missingness (mimicking the missing data in the original data set
before imputation). The resulting incomplete data can be accessed from
\href{https://zenodo.com}{zenodo link to be created}. TODO: email script
to thomas.

@@

This shows\ldots{} {[}TODO: fill in that we need to impute \texttt{ct}
and \texttt{pupil}.{]} TODO: remove axis labels
